---
title: "p8105_hw1_amr2371"
output: github_document
date: "2022-09-15"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r message=FALSE, results=FALSE}
library(tidyverse)
```

## Problem 1
```{r}
data("penguins", package = "palmerpenguins")
```
The penguins data set includes species, island, bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g, sex and year. Species and Island standout as important variables.

The data set contains `r nrow(penguins)` rows and `r ncol(penguins)` columns. Flipper length has a mean of `r mean(penguins$flipper_length_mm, na.rm=TRUE)`mm.

```{r warning=FALSE}
ggplot(penguins, aes(x=bill_length_mm, y=flipper_length_mm, color=species)) +
         geom_point()
```

```{r warning=FALSE}
ggsave("flipper_bill_scatterplot.pdf")
```

## Problem 2
```{r}
x_df = tibble(
  norm_samp = rnorm(10),
  vector_logic = norm_samp > 0,
  char_samp=c("this","is","an","assignment","for","my","data","science","one","class"),
  vector_factor = factor(c("car","bike","plane","bike","bike","car","plane","car","plane","bike"))
)

x_df

```
```{r}
mean(pull(x_df,1))
```

```{r}
mean(pull(x_df,2))
```

```{r}
mean(pull(x_df,3))
```

```{r}
mean(pull(x_df,4))
```
Taking the mean of the random sample gave the correct mean, and taking the mean of the logical vector gave a mean.Taking the mean of the character vector and the factor vector did not work.

```{r results=FALSE}
as.numeric(pull(x_df, 2))
as.numeric(pull(x_df, 3))
as.numeric(pull(x_df, 4))
```
When using the 'as.numeric' function, the logical vector is converted to 1 and 0 to represent True and False respectively so this is how the mean was calculated. The character variable is converted to NA since there is no way to assign a numeric value to characters. The factor vector is converted to 1, 2 or 3 since there are three levels, but they are still treated as character variables so R is unable to take the mean.
